---
title: "Impact of active learning on STEM achievement: Systematic review and new causal evidence"
author: "Prashant Loyalka, Mridul Joshi, Saurabh Khanna, and Paul Glewwe"
date: "18 November 2024"
output:
  html_document:
    toc: yes
    toc_depth: 6
    number_sections: yes
urlcolor: blue
---

\captionsetup[table]{labelformat=empty}


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, message = F, warning = F, fig.retina = 4)
```

```{r message=FALSE, warning=FALSE}
# Libraries
pacman::p_load(estimatr, texreg, janitor, tidyverse, skimr, compareGroups, BFpack, haven)
```

```{r}
# Filter coefficients that start with "fac_active"
custom_screen <- function(model) {
  coef_names <- names(coef(model))
  keep <- grepl("^fac_active", coef_names)  # Matches coefficients starting with "fac_active"
  coef_list <- coef_names[keep]
  setNames(coef_list, coef_list)  # Named list where names match values
}
```

# Experimental Sample

## Main effects

```{r}
df <- 
  read_csv("/Users/mriduljoshi/My Drive/Active Learning Paper/Replication/data/data_exp_sample.csv") 
```


```{r, results='asis'}
lme1 <-
  df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  lm_robust(course_rank ~ fac_active_teaching, data = ., fixed_effects = ~ fe_var, se_type = "stata", clusters = facultyid)

lme2 <-
  df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  lm_robust(course_rank ~ fac_active_teaching + female + ses + reservation_stu + rural + father_college + mother_college, data = ., fixed_effects = ~ fe_var, se_type = "stata", clusters = facultyid)

lme3 <-
  df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  lm_robust(course_rank ~ fac_active_teaching , data = ., fixed_effects = ~ studentid + fe_var, se_type = "stata", clusters = facultyid)

lme4 <-
  df %>% 
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  lm_robust(course_rank ~ fac_active_teaching  + female + ses + reservation_stu + rural + father_college + mother_college + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., fixed_effects = ~ fe_var, se_type = "stata", clusters = facultyid)

lme5 <-
  df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  lm_robust(course_rank ~ fac_active_teaching + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., fixed_effects = ~ studentid + fe_var, se_type = "stata", clusters = facultyid)

knitreg(list(lme1, lme2, lme3, lme4, lme5), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = TRUE, booktabs = TRUE, float.pos = "H", caption = "", digits = 3, include.rsquared = F, include.adjrs = F, include.rmse = F, include.nclust = F)

```

### Bayes Factor (main)

```{r}

calculate_bf <- function(model, model_name, hypothesis = "fac_active_teaching = 0") {
  cat(paste("Bayes Factor for", model_name, "\n"))
  BF(
    x = coef(model),
    Sigma = vcov(model),
    n = nobs(model),
    hypothesis = hypothesis
  ) %>% summary()
}

models <- list(lme1, lme2, lme3, lme4, lme5)

model_names <- c("M1", "M2", "M3", "M4", "M5")

invisible(mapply(calculate_bf, models, model_names))

```

\newpage

## Heterogeneous effects

```{r}
lme1a <-
  df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  filter(foundational==1) %>%
  lm_robust(course_rank ~ fac_active_teaching + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., fixed_effects = ~ studentid + fe_var, se_type = "stata", clusters = facultyid)

lme1b <-
  df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  filter(foundational==0) %>%
  lm_robust(course_rank ~ fac_active_teaching + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., fixed_effects = ~ studentid + fe_var, se_type = "stata", clusters = facultyid)

lme2a <-
  df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  filter(self_efficacy_lowest_tercile == 1) %>%
  lm_robust(course_rank ~ fac_active_teaching + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., fixed_effects = ~ studentid + fe_var, se_type = "stata", clusters = facultyid)

lme2b <-
  df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  filter(self_efficacy_lowest_tercile == 0) %>%
  lm_robust(course_rank ~ fac_active_teaching + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., fixed_effects = ~ studentid + fe_var, se_type = "stata", clusters = facultyid)

lme3a <-
  df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  filter(stem_anxiety_lowest_tercile == 1) %>%
  lm_robust(course_rank ~ fac_active_teaching + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., fixed_effects = ~ studentid + fe_var, se_type = "stata", clusters = facultyid)

lme3b <-
  df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  filter(stem_anxiety_lowest_tercile == 0) %>%
  lm_robust(course_rank ~ fac_active_teaching + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., fixed_effects = ~ studentid + fe_var, se_type = "stata", clusters = facultyid)


knitreg(list(lme1a, lme1b, lme2a, lme2b, lme3a, lme3b), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = TRUE, booktabs = TRUE, float.pos = "H", caption = "", digits = 3, include.rsquared = F, include.adjrs = F, include.rmse = F, include.nclust = F, custom.coef.map = list("fac_active_teaching" = "Active learning"), custom.model.names = c("Foundational", "Advanced", "Low self-efficacy", "High self-efficacy", "Low anxiety", "High anxiety"))

```

### Bayes Factor (het 1)

```{r}

calculate_bf <- function(model, model_name, hypothesis = "fac_active_teaching = 0") {
  cat(paste("Bayes Factor for", model_name, "\n"))
  BF(
    x = coef(model),
    Sigma = vcov(model),
    n = nobs(model),
    hypothesis = hypothesis
  ) %>% summary()
}

models <- list(lme1a, lme1b, lme2a, lme2b, lme3a, lme3b)

model_names <- c("Foundational", "Upperlevel", "Low efficacy", "High efficacy", "Low anxiety", "High anxiety")

invisible(mapply(calculate_bf, models, model_names))

```

Heterogeneity (student characteristics)

```{r, results='asis'}

lme4a <-
  df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  filter(female == 0) %>%
  lm_robust(course_rank ~ fac_active_teaching + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., fixed_effects = ~ studentid + fe_var, se_type = "stata", clusters = facultyid)

lme4b <-
  df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  filter(female == 1) %>%
  lm_robust(course_rank ~ fac_active_teaching + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., fixed_effects = ~ studentid + fe_var, se_type = "stata", clusters = facultyid)

lme5a <-
  df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  filter(ses_lowest_tercile == 0) %>%
   lm_robust(course_rank ~ fac_active_teaching + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., fixed_effects = ~ studentid + fe_var, se_type = "stata", clusters = facultyid)

lme5b <-
  df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  filter(ses_lowest_tercile == 1) %>%
  lm_robust(course_rank ~ fac_active_teaching + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., fixed_effects = ~ studentid + fe_var, se_type = "stata", clusters = facultyid)

lme6a <-
  df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  filter(jee_lowest_tercile == 0) %>%
   lm_robust(course_rank ~ fac_active_teaching + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., fixed_effects = ~ studentid + fe_var, se_type = "stata", clusters = facultyid)

lme6b <-
  df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  filter(jee_lowest_tercile == 1) %>%
  lm_robust(course_rank ~ fac_active_teaching + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., fixed_effects = ~ studentid + fe_var, se_type = "stata", clusters = facultyid)

lme7a <-
  df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  filter(rural == 0) %>%
  lm_robust(course_rank ~ fac_active_teaching + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., fixed_effects = ~ studentid + fe_var, se_type = "stata", clusters = facultyid)

lme7b <-
  df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  filter(rural == 1) %>%
  lm_robust(course_rank ~ fac_active_teaching + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., fixed_effects = ~ studentid + fe_var, se_type = "stata", clusters = facultyid)

lme8a <-
  df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  filter(reservation_stu == 0) %>%
  lm_robust(course_rank ~ fac_active_teaching + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., fixed_effects = ~ studentid + fe_var, se_type = "stata", clusters = facultyid)

lme8b <-
  df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  filter(reservation_stu == 1) %>%
  lm_robust(course_rank ~ fac_active_teaching + fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., fixed_effects = ~ studentid + fe_var, se_type = "stata", clusters = facultyid)

knitreg(list(lme4a, lme4b, lme5a, lme5b, lme6a, lme6b, lme7a, lme7b, lme8a, lme8b), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = TRUE, booktabs = TRUE, float.pos = "H", caption = "", digits = 3, include.rsquared = F, include.adjrs = F, include.rmse = F, include.nclust = F, custom.coef.map = list("fac_active_teaching" = "Active learning"), custom.model.names = c("Male", "Female", "High/medium SES", "Low SES", "High JEE", "Low JEE", "Urban", "Rural", "Non-reservation", "Reservation"))
```

\newpage

### Bayes Factor


```{r}

calculate_bf <- function(model, model_name, hypothesis = "fac_active_teaching = 0") {
  cat(paste("Bayes Factor for", model_name, "\n"))
  BF(
    x = coef(model),
    Sigma = vcov(model),
    n = nobs(model),
    hypothesis = hypothesis
  ) %>% summary()
}

models <- list(lme4a, lme4b, lme5a, lme5b, lme6a, lme6b, lme7a, lme7b, lme8a, lme8b)

model_names <- c("Male", "Female", "High SES", "Low SES", "High JEE", "Low JEE", "Urban", "Rural", "Non-res", "Res")

invisible(mapply(calculate_bf, models, model_names))

```

## Table E3

### Student characteristics

```{r}
df %>%
  distinct(studentid, .keep_all = T) %>%
  skim(female, rural, reservation_stu, father_college, mother_college)
```

Balance:

```{r, results='asis'}
lmbal1 <- df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  lm_robust(female ~ fac_active_teaching, data = ., fixed_effects = ~ fe_var, se_type = "stata", clusters = facultyid)

lmbal2 <-df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  lm_robust(rural ~ fac_active_teaching, data = ., fixed_effects = ~ fe_var, se_type = "stata", clusters = facultyid) 

lmbal3 <-df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  lm_robust(reservation_stu ~ fac_active_teaching, data = ., fixed_effects = ~ fe_var, se_type = "stata", clusters = facultyid) 

lmbal4 <-df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  lm_robust(father_college ~ fac_active_teaching, data = ., fixed_effects = ~ fe_var, se_type = "stata", clusters = facultyid) 

lmbal5 <-df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  lm_robust(mother_college ~ fac_active_teaching, data = ., fixed_effects = ~ fe_var, se_type = "stata", clusters = facultyid) 


knitreg(list(lmbal1, lmbal2, lmbal3, lmbal4, lmbal5), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = TRUE, booktabs = TRUE, float.pos = "H", caption = "", digits = 3, include.rsquared = F, include.adjrs = F, include.rmse = F, include.nclust = F)

```

# Joint test

```{r}

df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  lm_robust(fac_active_teaching ~  female + rural + reservation_stu + father_college + mother_college, data = ., fixed_effects = ~ fe_var, se_type = "stata", clusters = facultyid) %>%
  summary()

```

### Faculty characteristics

```{r}
df %>%
  distinct(facultyid, .keep_all = T) %>%
  skim(fac_associate_professor, fac_professor, fac_yearsinhighed, fac_highest_degree_phd, fac_highest_degree_phd_in_prog, fac_degree_college_elite, fac_female)
```

Balance:

```{r, results='asis'}
lmbalf1 <- df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  lm_robust(fac_associate_professor ~ fac_active_teaching, data = ., fixed_effects = ~ fe_var, se_type = "stata", clusters = facultyid)

lmbalf2 <-df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  lm_robust(fac_professor ~ fac_active_teaching, data = ., fixed_effects = ~ fe_var, se_type = "stata", clusters = facultyid) 

lmbalf3 <-df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  lm_robust(fac_yearsinhighed ~ fac_active_teaching, data = ., fixed_effects = ~ fe_var, se_type = "stata", clusters = facultyid) 

lmbalf4 <-df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  lm_robust(fac_highest_degree_phd ~ fac_active_teaching, data = ., fixed_effects = ~ fe_var, se_type = "stata", clusters = facultyid) 

lmbalf5 <-df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  lm_robust(fac_highest_degree_phd_in_prog ~ fac_active_teaching, data = ., fixed_effects = ~ fe_var, se_type = "stata", clusters = facultyid) 

lmbalf6 <-df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  lm_robust(fac_degree_college_elite ~ fac_active_teaching, data = ., fixed_effects = ~ fe_var, se_type = "stata", clusters = facultyid) 

lmbalf7 <-df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  lm_robust(fac_female ~ fac_active_teaching, data = ., fixed_effects = ~ fe_var, se_type = "stata", clusters = facultyid) 


knitreg(list(lmbalf1, lmbalf2, lmbalf3, lmbalf4, lmbalf5, lmbalf6, lmbalf7), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = F, dcolumn = TRUE, booktabs = TRUE, float.pos = "H", caption = "", digits = 3, include.rsquared = F, include.adjrs = F, include.rmse = F, include.nclust = F)

```

```{r}
df %>%
  mutate(fe_var = str_c(departmentid, coursename, sep = "_")) %>%
  lm_robust(fac_active_teaching ~ fac_associate_professor + fac_professor + fac_yearsinhighed + fac_highest_degree_phd + fac_highest_degree_phd_in_prog + fac_degree_college_elite + fac_female, data = ., fixed_effects = ~ fe_var, se_type = "stata", clusters = facultyid) %>%
  summary()
```

\newpage

# Cross-country sample

## Main effects

```{r}
#df <- read_csv("data_crosscountry_sample_v3.csv")
df <- read_csv("/Users/mriduljoshi/My Drive/Active Learning Paper/Replication/ActiveLearning_Data_and_code/data_qexp_sample.csv")
```

```{r, results='asis'}
lmq1 <-
  df %>% 
  filter(country == "China") %>%
  lm_robust(g3_score ~ active_score + g1_score + bfac_yearsinhighed + bfac_degree_college_elite + bfac_degree_univ_elite + bfac_publications + bfac_female + bfac_highest_degree_phd + bfac_professor + bfac_associate_professor, fixed_effects = ~ studentid, data = ., clusters = departmentid, se_type = "stata")

lmq2 <-
  df %>%
  filter(country == "India") %>%
  lm_robust(g3_score ~ active_score + g1_score + bfac_yearsinhighed + bfac_degree_college_elite + bfac_degree_univ_elite + bfac_publications + bfac_female + bfac_highest_degree_phd + bfac_professor + bfac_associate_professor, fixed_effects = ~ studentid, data = ., clusters = departmentid, se_type = "stata")

lmq3 <-
  df %>%
  filter(country == "Russia") %>%
    lm_robust(g3_score ~ active_score + g1_score + bfac_yearsinhighed  + bfac_publications + bfac_female + bfac_highest_degree_phd + bfac_professor + bfac_associate_professor, fixed_effects = ~ studentid, data = ., clusters = departmentid, se_type = "stata")

knitreg(list(lmq1, lmq2, lmq3), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = FALSE, custom.model.names = c("China", "India", "Russia"), dcolumn = TRUE, booktabs = TRUE, float.pos = "H", caption = "", digits = 3, include.rsquared = F, include.adjrs = F, include.rmse = F, include.nclust = F, custom.coef.names = c("Active learning", "Baseline achievement", "Faculty experience", "Faculty undergrad from elite college", "Faculty graduate from elite college", "Faculty total publications", "Faculty female", "Faculty highest degree is PhD", "Professor", "Associate Professor"), custom.coef.map = list("active_score" = "Active learning"))
```


\newpage

### Bayes Factor

```{r}

calculate_bf <- function(model, model_name, hypothesis = "active_score = 0") {
  cat(paste("Bayes Factor for", model_name, "\n"))
  BF(
    x = coef(model),
    Sigma = vcov(model),
    n = nobs(model),
    hypothesis = hypothesis
  ) %>% summary()
}


models <- list(lmq1, lmq2, lmq3)

model_names <- c("China", "India", "Russia")

invisible(mapply(calculate_bf, models, model_names))

```

## Heterogeneity

### By gender

```{r, results='asis'}
lmq1a <-
  df %>%
  filter(country == "India", female == 1) %>%
  lm_robust(g3_score ~ active_score + g1_score + bfac_yearsinhighed + bfac_degree_college_elite + bfac_degree_univ_elite + bfac_publications + bfac_female + bfac_highest_degree_phd + bfac_professor + bfac_associate_professor, fixed_effects = ~ studentid, data = ., clusters = departmentid, se_type = "stata")

lmq1b <-
  df %>%
  filter(country == "India", female == 0) %>% 
  lm_robust(g3_score ~ active_score + g1_score + bfac_yearsinhighed + bfac_degree_college_elite + bfac_degree_univ_elite + bfac_publications + bfac_female + bfac_highest_degree_phd + bfac_professor + bfac_associate_professor, fixed_effects = ~ studentid, data = ., clusters = departmentid, se_type = "stata")

lmq2a <-
  df %>%
  filter(country == "China", female == 1) %>% 
  lm_robust(g3_score ~ active_score + g1_score + bfac_yearsinhighed + bfac_degree_college_elite + bfac_degree_univ_elite + bfac_publications + bfac_female + bfac_highest_degree_phd + bfac_professor + bfac_associate_professor, fixed_effects = ~ studentid, data = ., clusters = departmentid, se_type = "stata")

lmq2b <-
  df %>%
  filter(country == "China", female == 0) %>% 
  lm_robust(g3_score ~ active_score + g1_score + bfac_yearsinhighed + bfac_degree_college_elite + bfac_degree_univ_elite + bfac_publications + bfac_female + bfac_highest_degree_phd + bfac_professor + bfac_associate_professor, fixed_effects = ~ studentid, data = ., clusters = departmentid, se_type = "stata")

lmq3a <-
  df %>%
  filter(country == "Russia", female == 1) %>% 
  lm_robust(g3_score ~ active_score + g1_score + bfac_yearsinhighed  + bfac_publications + bfac_female + bfac_highest_degree_phd + bfac_professor + bfac_associate_professor, fixed_effects = ~ studentid, data = ., clusters = departmentid, se_type = "stata")

lmq3b <-
  df %>%
  filter(country == "Russia", female == 0) %>% 
  lm_robust(g3_score ~ active_score + g1_score + bfac_yearsinhighed + bfac_publications + bfac_female + bfac_highest_degree_phd + bfac_professor + bfac_associate_professor, fixed_effects = ~ studentid, data = ., clusters = departmentid, se_type = "stata")

knitreg(list(lmq1a, lmq1b, lmq2a, lmq2b, lmq3a, lmq3b), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = FALSE, custom.model.names = c("India Female", "India Male", "China Female", "China Male", "Russia Female", "Russia Male"), dcolumn = TRUE, booktabs = TRUE, float.pos = "H", caption = "", digits = 3, include.rsquared = F, include.nclust = F, include.adjrs = F, include.rmse = F, custom.coef.names = c("Active learning", "Baseline achievement", "Faculty experience", "Faculty undergrad from elite college", "Faculty graduate from elite college", "Faculty total publications", "Faculty female", "Faculty highest degree is PhD", "Professor", "Associate Professor"), custom.coef.map = list("active_score" = "Active learning"))
```

\newpage

#### Bayes Factor

```{r}

calculate_bf <- function(model, model_name, hypothesis = "active_score = 0") {
  cat(paste("Bayes Factor for", model_name, "\n"))
  BF(
    x = coef(model),
    Sigma = vcov(model),
    n = nobs(model),
    hypothesis = hypothesis
  ) %>% summary()
}

models <- list(lmq1a, lmq1b, lmq2a, lmq2b, lmq3a, lmq3b)

model_names <- c("India F", "India M", "China F", "China M", "Russia F", "Russia M")

invisible(mapply(calculate_bf, models, model_names))


```


### By socioeconomic status

```{r, results='asis'}
lmq4a <-
  df %>%
  filter(country == "India", ses_lowest_tercile == 0) %>% 
  lm_robust(g3_score ~ active_score + g1_score + bfac_yearsinhighed + bfac_degree_college_elite + bfac_degree_univ_elite + bfac_publications + bfac_female + bfac_highest_degree_phd + bfac_professor + bfac_associate_professor, fixed_effects = ~ studentid, data = ., clusters = departmentid, se_type = "stata")

lmq4b <-
  df %>%
  filter(country == "India", ses_lowest_tercile == 1) %>% 
  lm_robust(g3_score ~ active_score + g1_score + bfac_yearsinhighed + bfac_degree_college_elite + bfac_degree_univ_elite + bfac_publications + bfac_female + bfac_highest_degree_phd + bfac_professor + bfac_associate_professor, fixed_effects = ~ studentid, data = ., clusters = departmentid, se_type = "stata")

lmq5a <-
  df %>%
  filter(country == "China", ses_lowest_tercile == 0) %>% 
  lm_robust(g3_score ~ active_score + g1_score + bfac_yearsinhighed + bfac_degree_college_elite + bfac_degree_univ_elite + bfac_publications + bfac_female + bfac_highest_degree_phd + bfac_professor + bfac_associate_professor, fixed_effects = ~ studentid, data = ., clusters = departmentid, se_type = "stata")

lmq5b <-
  df %>%
  filter(country == "China", ses_lowest_tercile == 1) %>% 
  lm_robust(g3_score ~ active_score + g1_score + bfac_yearsinhighed + bfac_degree_college_elite + bfac_degree_univ_elite + bfac_publications + bfac_female + bfac_highest_degree_phd + bfac_professor + bfac_associate_professor,fixed_effects = ~ studentid, data = ., clusters = departmentid, se_type = "stata")

lmq6a <-
  df %>%
  filter(country == "Russia", ses_lowest_tercile == 0) %>% 
  lm_robust(g3_score ~ active_score + g1_score + bfac_yearsinhighed + bfac_publications + bfac_female + bfac_highest_degree_phd + bfac_professor + bfac_associate_professor, fixed_effects = ~ studentid, data = ., clusters = departmentid, se_type = "stata")

lmq6b <-
  df %>%
  filter(country == "Russia", ses_lowest_tercile == 1) %>%
  lm_robust(g3_score ~ active_score + g1_score + bfac_yearsinhighed + bfac_publications + bfac_female + bfac_highest_degree_phd + bfac_professor + bfac_associate_professor, fixed_effects = ~ studentid, data = ., clusters = departmentid, se_type = "stata")

knitreg(list(lmq4a, lmq4b, lmq5a, lmq5b, lmq6a, lmq6b), custom.note = "%stars", stars = c(0.01, 0.05, 0.1), include.ci = FALSE, custom.model.names = c("India High SES", "India Low SES", "China High SES", "China Low SES", "Russia High SES", "Russia Low SES"), dcolumn = TRUE, booktabs = TRUE, float.pos = "H", caption = "", digits = 3, include.rsquared = F, include.adjrs = F, include.nclust = F, include.rmse = F, custom.coef.names = c("Active learning", "Baseline achievement", "Faculty experience", "Faculty undergrad from elite college", "Faculty graduate from elite college", "Faculty total publications", "Faculty female", "Faculty highest degree is PhD", "Professor", "Associate Professor"), custom.coef.map = list("active_score" = "Active learning"))
```


\newpage

#### Bayes Factor

```{r}


calculate_bf <- function(model, model_name, hypothesis = "active_score = 0") {
  cat(paste("Bayes Factor for", model_name, "\n"))
  BF(
    x = coef(model),
    Sigma = vcov(model),
    n = nobs(model),
    hypothesis = hypothesis
  ) %>% summary()
}

models <- list(lmq4a, lmq4b, lmq5a, lmq5b, lmq6a, lmq6b)

model_names <- c("India high", "India low", "China high", "China low", "Russia high", "Russia low")

invisible(mapply(calculate_bf, models, model_names))


```

## Table E4: Summary statistics

```{r, results='asis'}
df %>% 
  distinct(studentid, .keep_all = T) %>%
  compareGroups(country ~ female + age_years + father_college + mother_college, data = ., include.label = F) %>%   
  createTable(show.all = F, show.n = F, show.p.overall = F, digits = 3)

```
